---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
<!-- badges: start -->
[![Travis build status](https://travis-ci.org/news-r/greatfire.svg?branch=master)](https://travis-ci.org/news-r/greatfire)
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/news-r/greatfire?branch=master&svg=true)](https://ci.appveyor.com/project/news-r/greatfire)
<!-- badges: end -->

# greatfire

Datasets of keywords and urls censored on the Chinese internet, taken from [greatfire.org](https://en.greatfire.org/)

## :construction: Note

Though not publicly mentioned [greatfire.org](https://en.greatfire.org/) has an API publicly available, it's not difficult to uncover. However, as I very much appreciate their project this package does not provide direct access to it and instead provides two datasets that I pledge to keep updated. If it is too outdated please open an issue.

Last updated: `r Sys.time()`

## Installation

You can install `greatfire` from Github using via the `remotes` or `devtools` package.

``` r
# install.packages("remotes")
remotes::install_github("news-r/greatfire")
```

## Example

Both datasets are rather large and therefore not lazily loaded, you therefore have to explicitly call the `data` function.

```{r}
library(greatfire)

data(censored_keywords)
dim(censored_keywords)
head(censored_keywords)

data(censored_urls)
dim(censored_urls)
head(censored_urls)
```
